Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Finish comments complexity subsection

More specifically, we computed the following numbers for the tickets we collected:
\begin{itemize}
  \item out of the 303,138 tickets, 236,383 tickets have been closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
  fetched them from the Jira instance;
  \item 287,120 tickets are of high priority (i.e. marked as Blocker, Critical, Major or High);
  \item 103,397 tickets have attachments which we split in the following categories:
    \begin{itemize}
      \item 4,082 have code attachments (e.g. Go, Java, Python);
      \item 7,171 have image attachments (e.g. png, jpg/jpeg, gif);
      \item 164 have video attachments (e.g. mkv, avi, mp4);
      \item 13,990 have text attachments (e.g. txt, md, doc(x));
      \item 918 have config attachments (e.g. json, xml, yml);
      \item 2,491 have archive attachments (e.g. zip, tar.gz, rar, 7z);
      \item 280 have spreadsheet attachments (e.g. csv, xlsx);
      \item 80,015 have other attachments (i.e. any file extension not pre-defined by us in one of the above categories).
    \end{itemize}
  \item 270,907 tickets have comments;
  \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
  \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et. al 
  \cite{bettenburg2008extracting} for extracting structured data from bug reports and even though the method proved to be efficient, 
  the total number of stack traces is so small due to the fact that many projects are actually written in languages other than Java;
  \item 133,689 tickets have grammar correctness scores (i.e. number of grammar mistakes inside summary, description and comments) - 
  they have been collected using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
  \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs.
\end{itemize}

@@

Attachments are, as mentioned previously, files attached to software tickets that can take any form - from code 
snippets written in Java to tar archives. We have analyzed all tickets that were both of high priority tickets and
were marked as Closed by the time we collected the data. Then we split all these tickets into two main categories: 
with attachments and without attachments. Furthermore, the tickets that were marked as having attachments were split 
into the categories specified in Section \ref{characterising}.

@@

Figure \ref{steps} shows the bar chart representing all closed, high priority tickets with or without steps 
to reproduce in either the description field or in any of the comments.

@@

For this analysis, we only looked at tickets of high priority, closed and the project they correspond 
is written in Java. We then ran a complex regular expression derived from the works of Bettenburg et. al 
\cite{bettenburg2012using} and Moreno et. al \cite{moreno2014use} and collected all the tickets that have 
stack traces. In the end, we got a total number of 256 tickets that had at least an exception stack trace 
attached in either summary, description or any of the comments.

@@

@@

>>>>

More specifically, we computed the following numbers for the tickets we collected:
\begin{itemize}
  \item out of the 303,138 tickets, 236,383 tickets have been closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
  fetched them from the Jira instance;
  \item 287,120 tickets are of high priority (i.e. marked as Blocker, Critical, Major or High);
  \item 201,786 tickets have all our requirements for running the analysis: were closed by the time we fetched the data, 
  are of high priority and are not \emph{wrong} values retrieved from Jira (i.e. outliers);
  \item 103,397 tickets have attachments which we split in the following categories:
    \begin{itemize}
      \item 4,082 have code attachments (e.g. Go, Java, Python);
      \item 7,171 have image attachments (e.g. png, jpg/jpeg, gif);
      \item 164 have video attachments (e.g. mkv, avi, mp4);
      \item 13,990 have text attachments (e.g. txt, md, doc(x));
      \item 918 have config attachments (e.g. json, xml, yml);
      \item 2,491 have archive attachments (e.g. zip, tar.gz, rar, 7z);
      \item 280 have spreadsheet attachments (e.g. csv, xlsx);
      \item 80,015 have other attachments (i.e. any file extension not pre-defined by us in one of the above categories).
    \end{itemize}
  \item 270,907 tickets have comments;
  \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
  \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et. al 
  \cite{bettenburg2008extracting} for extracting structured data from bug reports and even though the method proved to be efficient, 
  the total number of stack traces is so small due to the fact that many projects are actually written in languages other than Java;
  \item 133,689 tickets have grammar correctness scores (i.e. number of grammar mistakes inside summary, description and comments) - 
  they have been collected using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
  \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs.
\end{itemize}

@@

Attachments are, as mentioned previously, files attached to software tickets that can take any form - from code 
snippets written in Java to tar archives. We have analyzed all tickets that were both of high priority tickets and
were marked as Closed by the time we collected the data. Then we split all these tickets into two main categories: 
with attachments and without attachments. Furthermore, the tickets that were marked as having attachments were split 
into the categories specified in Section \ref{characterising}. In total, we looked at 201,786 tickets, among which 
98,311 had attachments and 103,475 without any attachments.

@@

Figure \ref{steps} shows the bar chart representing all closed, high priority tickets with or without steps 
to reproduce in either the description field or in any of the comments. We looked in total at 201,786 tickets 
among which 31,732 tickets had steps to reproduce and 170,054 did not have.

@@

For this analysis, we only looked at tickets of high priority, closed and the project they correspond 
is written in Java. In total, we investigated looked at We then ran a complex regular expression derived from the works of Bettenburg et. al 
\cite{bettenburg2012using} and Moreno et. al \cite{moreno2014use} and collected all the tickets that have 
stack traces. In the end, we got a total number of 256 tickets that had at least an exception stack trace 
attached in either summary, description or any of the comments.

@@

The comment field is comprised of a textual body, a corresponding author, its time of creation and any updates 
that were performed on it throughout its lifecycle. They provide a space for developers and end users to discuss 
anything related to the ticket they belong to. Any popular issue tracking system, such as Jira, does not enforce 
any limit on any component of a comment, thus the number of words for a single comment can range from only 5 
to well over 1,000.

We firstly concatenated all comments into a single large string in order to be analysed for total number of words.
We ran our comments analysis on 201,786 tickets among which 113,344 had comments and 88,442 did not have any comments.

In Figure \ref{comments} we present the correlations between the total number of words in comments per ticket and 
the corresponding Time-To-Close for that ticket. We can observe in the scatter plot that most tickets tend to 
have up to around 3,200 words in total. However, there are tickets that have a total number of words as high as 
around 25,000.

From the figure we cannot clearly deduce whether increased number of words in comments influence 
the Time-To-Close positively or negatively. However, a correlational analysis releaved a weak 
positive relationship with $r = 0.271$ and $p < 0.01$. This implies a statistically significant finding - 
as the number of comments increases, the quality of the ticket decreases.

Even though this might be surprising at first, we need to analyse the possible context where such large 
number of words in comments occur. What if the bug was so hard to reproduce that the developers needed to 
ask more than one user how they experienced the issue in the tool? Another case might be that even though 
the comments start by discussing fixing or implementing a feature, the developers and end users might 
engage in new conversations about the product in general or other features that they might want to see 
implemented. Also, what if comments are a means of communication for developers in the team? There are studies, 
such as the one conducted by Lotufo et. al \cite{lotufo2015modelling}, that show the importance of comments 
in software tickets in relation to communication activities surrounding the project. Another possible explanation 
for having increased number of comments increase the Time-To-Close value and, thus, decrease quality, is that 
having many comments or very verbose comment can lead to more difficult information extraction. On the other 
hand, if there would be a light discussion, the developers would be able to quickly analyse all the comments 
and collect whatever is necessary to resolve the ticket.

One possible solution that we propose to this correlation is to have the ability to limit the number of 
comments per ticket. As to our knowledge, one cannot do this in neither Jira nor Bugzilla. However, if it were 
possible, we believe that this might help developers find the information they need quicker. But what happens 
if the treshold is reached and there is still a need for clarifying certain aspects? We believe that having 
a button redirecting anyone still interesting in commenting on the ticket to a messaging tool, such as 
Slack, would be beneficial for the project overall. Thus, if they were redirected to let's say Slack, a small 
tool could automatically be run that creates a new channel specifically for that ticket with the name set 
to the unique ticket key (e.g. LUCENE-2901). We believe that such a solution could aid both developers in 
completing tasks quicker but also end users for feeling more involved and valuable to the project.

@@

Summary and description are the two most important and most frequently completed fields in a ticket on any
issue tracking system. Even though summary is required on any issue tracking system, description might 
be omitted if the reporter does not feel the need of adding any extra detail other than what is in the summary. 
However, as bug reports are usually complex, there is a very small percentage of descriptions not filled in 
by the reporters. They do not typically have any word limits, thus the reporter can add as much information as 
they see fit.

Figure \ref{fields} shows the scatter plot for the sum of numbers of words in summary and description, as well 
as the Time-To-Close for the ticket. We have analysed a total number of 238,286 (all our closed tickets as they 
all have), all having both summaries and descriptions.

From the
